Blum axioms and nondeterministic computation of functions

### 2015-12-16 paper.tex
paper.tex: Show the Blum axioms are independent.

>>>>

\begin{example}
    Choosing $\Phi(w, x) = 0$ for all $w$ and $x$
    creates a function that satisfies the second axiom,
    but not the first.
    Leaving $\Phi(w, x)$ undefined for all $w$ and $x$ such that
    $\pi_w(x)$ does not exists and defining $\Phi(w, x) = 0$ otherwise
    satisfies the first axiom, but not the second.
    This shows the axioms are independent \cite[p.~324]{Blum1967}.
\end{example}
